```{r apis-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, collapse = TRUE, comment = ">")
```

class: inverse, center, middle

# Accessing web APIs

---

# Some background

 **Application Program Interfaces** (APIs) are sets of protocols that govern interactions between sites and users.

APIs are similar to web browsers but with different purpose:
- Web browsers **render** content
- Web APIs manage and organize **data**


For public APIs, many sites only allow **authorized** users
- Twitter, Facebook, Instagram, Github, etc.

---

# Twitter APIs

To connect to Twitter's APIs, users need a **consumer key** and **consumer secret**, which you can get by creating a Twitter app.

View the built-in vignette **`auth`** for instructions on obtaining and storing user access tokens.<sup>\* </sup>

```{r}
## view rtweet's authorization vignette
vignette("auth", package = "rtweet")
```

Or look up the vignette online: [rtweet.info/articles/auth.html](http://rtweet.info/articles/auth.html)

.footnote[
<sup> \* </sup> For a while, rtweet users were not required to create their own Twitter applications. [That recently changed](https://github.com/mkearney/rtweet/issues/179#issuecomment-365689068), but hopefully it's resolved soon.
]
